RadLib: a radiative heat transfer model library for CFD

### 2020-12-16 manuscript/manuscript.tex
Added soot treatment subsection to model description

The RCSLW model begins with the SLW form of the RTE, given by Equation \ref{e:RTE_SLW}. The gray gas absorption coefficients $\kappa_j$ are calculated calculated as $\kappa_j=N \sqrt{C_{j-1}C_j}$,
where $C_{j-1}$ and $C_j$ are supplemental absorption cross-sections used to discretize the absorption spectrum \cite{Solovjov_2001}. The gray gas weights $a_j$ corresponding to each absorption coefficient are given by $a_j=F(C_j)-F(C_{j-1})$, where $F(C_j)$ is the absorption line blackbody distribution function (ALBDF) for species $j$, calculated from the detailed absorption spectrum of that species. In general SLW methods, the absorption cross-sections are chosen with respect to a thermodynamic reference state, classifying them as reference approaches. The Rank-Correlated SLW (RCSLW) model avoids specifying a reference state by relating thermodynamic states to one another instead. If two arbitrary absorption cross-sections define identical wavenumber intervals, the two cross-sections (neither of which is designated a reference cross-section) can be said to be rank-correlated. The inverse ALBDF, defined such that $C[F(C,\phi_g,T_b),\phi_g,T_b]=C$ and $F[C(F,\phi_g,T_b),\phi_g,T_b]=F$ for a given gas thermodynamic state $\phi_g$ and blackbody temperature $T_b$, is proven to have this property and can also be called the rank-correlated reordered absorption cross-sections \cite{Solovjov_2017}. As a result, the inverse ALBDF can be used to construct cross-section intervals for the RCSLW model that do not rely on an arbitrary reference state or spectrum. RadLib's RCSLW model uses Method 1.2.2 as defined and recommended in \cite{Solovjov_2017}.

>>>>

The RCSLW model begins with the SLW form of the RTE, given by Equation \ref{e:RTE_SLW}. The gray gas absorption coefficients $\kappa_j$ are calculated calculated as $\kappa_j=N \sqrt{C_{j-1}C_j}$,
where $C_{j-1}$ and $C_j$ are supplemental absorption cross-sections used to discretize the absorption spectrum \cite{Solovjov_2001}. The gray gas weights $a_j$ corresponding to each absorption coefficient are given by $a_j=F(C_j)-F(C_{j-1})$, where $F(C_j)$ is the absorption line blackbody distribution function (ALBDF) for species $j$, calculated from the detailed absorption spectrum of that species. In general SLW methods, the absorption cross-sections are chosen with respect to a thermodynamic reference state, classifying them as reference approaches. The Rank-Correlated SLW (RCSLW) model avoids specifying a reference state by relating thermodynamic states to one another instead. If two arbitrary absorption cross-sections define identical wavenumber intervals, the two cross-sections (neither of which is designated a reference cross-section) can be said to be rank-correlated. The inverse ALBDF, defined such that $C[F(C,\phi_g,T_b),\phi_g,T_b]=C$ and $F[C(F,\phi_g,T_b),\phi_g,T_b]=F$ for a given gas thermodynamic state $\phi_g$ and blackbody temperature $T_b$, is proven to have this property and can also be called the rank-correlated reordered absorption cross-sections \cite{Solovjov_2017}. As a result, the inverse ALBDF can be used to construct cross-section intervals for the RCSLW model that do not rely on an arbitrary reference state or spectrum. ALBDFs for individual gray gases are multiplied together to obtain an overall ABLDF for the gas mixture \cite{Solovjov_2001}. RadLib's RCSLW model uses Method 1.2.2 as defined in and recommended by \cite{Solovjov_2017}.

\subsection{Soot treatment}
\label{s:soot}

RadLib can also account for the radiative properties of soot in combustion environments. Soot particles are assumed to be unagglomerated spheres that absorb and emit radiation at all wavelengths such that their optical properties can be determined using the Rayleigh small particle limit. Radiation scattering may be neglected because unagglomerated soot particles in the Rayleigh regime are still small relative to the wavelength of infrared radiation in flames \cite{Brewster_1992,Solovjov_2001}. The spectral soot absorption coefficient is given by 
\begin{equation}
\label{e:soot1}
	\kappa_{\lambda}=C_0 \frac{f_v}{\lambda} , \; \; \; C_0 = \frac{36\pi n k}{(n^2-k^2+2)^2+4n^2k^2},
\end{equation}
where $n$ and $k$ are the real and imaginary parts of the soot complex index of refraction, respectively, and $f_v$ is the soot volume fraction \cite{Solovjov_2001,Modest_2013}. Various values for the refraction index have been proposed and applied to various scenarios \cite{Lee_1981,Stull_1960,Dalzell_1969,Howarth_1966,Chang_1990,Felske_1984,Williams_2007}. RadLib uses the values $n=1.75$ and $k=1.03$ given in \cite{Williams_2007}, which result in a value of $C_0=7.03$, aligning nicely with the value $C_0=7.0$ suggested by \cite{Solovjov_2001}. Due to the simple $1/\lambda$ dependence and the suitably small difference between the mean absorption coefficients calculated for optically thin and optically thick cases, we can use one expression to calculate a spectral mean absorption coefficient for soot that applies to all optical regimes:
\begin{equation}
\label{e:soot2}
	\kappa_{soot}=3.72\frac{f_vC_0T}{C_2},
\end{equation}
where $T$ is the temperature and $C_2=1.4388$ cm K is a Planck function constant \cite{Modest_2013}.

In order to incorporate its radiative effects, soot is modeled as a pseudo-gas of its own and included alongside the existing gray gases. In the Planck Mean model, which models a gas mixture as one gray gas, the soot absorption coefficient calculated from Equation \ref{e:soot2} is simply added to the existing gas absorption coefficient. In the WSGG model, the soot absorption coefficient is similarly calculated from Equation \ref{e:soot2} but is then added to each of the gases separately. Because soot radiates across all wavelengths, its absorption coefficient is added to the values of all four gray gases and the transparent gas that represents the spectral gaps between absorption bands. Unlike the Planck Mean and WSGG models, the RCSLW model requires a spectrally dependent soot model. Instead of finding a mean soot absorption coefficient, we use Equation \ref{e:soot1} to define a soot absorption cross-section and ALBDF as detailed in \cite{Solovjov_2001}. The soot ALBDF can then be multiplied with the other gray gas ALBDFs to find the overall ALBDF for the gas-soot mixture.
